### 2019-04-27 Thesis/games.tex
Monthly commit.

\begin{definition}[Equational Soundness Result]
  An \emph{inequational soundness result} for a semantics as above is a result that says that if $M,N\from T$ are such that $\deno{M}\sim\deno{N}$, then $M$ and $N$ are observationally equivalent.
\end{definition}

\begin{proposition}
  Any semantics satisfying Computational Adequacy satisfies Inequational Soundness.
\end{proposition}
\begin{proof}
  Suppose that $\deno{M}\sim\deno{N}$.  
  Let $C[-]\from o$ be a context with a hole of type $T$.
  Then, since $\C$ is Cartesian closed, the $\beta$-rule is valid in $\C$, and therefore we have
  \[
    \deno{C[M]} = 1 \xrightarrow{\deno{M}} \deno{T} \xrightarrow{\deno{x\from T\ts C[x]}} \deno{o}\,,
    \]
  and similarly for $C[N]$.  
  Therefore, taking $\alpha=\deno{x\ts C[x]}$ in the definition of $\sim$, we get that $\deno{C[M]}\downarrow$ if and only if $\deno{C[N]}\downarrow$.  
  By Computational Adequacy, this means that $C[M]\converges$ if and only if $C[N]\converges$.  
  Since $C$ was arbitrary, it follows that $M$ and $N$ are observationally equivalent.
\end{proof}

>>>>

\begin{definition}[Equational Soundness Result]
  An \emph{equational soundness result} for a semantics as above is a result that says that if $M,N\from T$ are such that $\deno{M}\sim\deno{N}$, then $M$ and $N$ are observationally equivalent.
\end{definition}

\begin{proposition}
  Any semantics satisfying Computational Adequacy satisfies Equational Soundness.
  \label{PropEquationalSoundness}
\end{proposition}
\begin{proof}
  Suppose that $\deno{M}\sim\deno{N}$.  
  Let $C[-]\from o$ be a context with a hole of type $T$.
  Then, since $\C$ is Cartesian closed, the $\beta$-rule is valid in $\C$, and therefore we have
  \[
    \deno{C[M]} = 1 \xrightarrow{\deno{M}} \deno{T} \xrightarrow{\deno{x\from T\ts C[x]}} \deno{o}\,,
    \]
  and similarly for $C[N]$.  
  Therefore, taking $\alpha=\deno{x\ts C[x]}$ in the definition of $\sim$, we get that $\deno{C[M]}\downarrow$ if and only if $\deno{C[N]}\downarrow$.  
  By Computational Adequacy, this means that $C[M]\converges$ if and only if $C[N]\converges$.  
  Since $C$ was arbitrary, it follows that $M$ and $N$ are observationally equivalent.
\end{proof}
